There are no small Advantages: Reinforcement learning in near continuous time with Deep RelAtive Mixture of Advantages

### 2019-01-11 paper/icml_drau/advup.tex
Update.

\subsection{Algorithms}
\label{subsec:algorithm}
To learn $V_{\theta}$ and $A_{\psi}$, variants of Q-learning for continuous~\cite{ddpg} and
discrete~\cite{dqn} action spaces are used. In details, $V_{\theta}$ and $A_{\psi}$ are learnt
using approximate version of the following bellman equation
\begin{align}
	V^{\pi}_\deltat(s) + A^{\pi}_\deltat(s, a) &= \E_{\delta r \sim \delta r(s, a)}\delta r\nonumber\\ 
				   &+ \gamma^{\deltat}  \E_{\delta s \sim \delta s(s, a)} V^{\pi}_\deltat(s + \delta s)\label{eq:bellman_A}\\
	A^{\pi}_\deltat(s, \pi(s)) &= 0\label{eq:max_A}
\end{align}
for a greedy exploitation policy $\pi(s) = \text{argmax}_{a'}A^\pi_\deltat(s, a')$,
exactly implemented in the case of discrete actions, and approximated by a
neural network $\pi_\phi(s)$, trained to maximize (an approximation of)
$A^\pi_\deltat(s, \pi_\phi(s))$ in the continuous case.  Eq.~\eqref{eq:max_A} is
directly verified by $A_{\theta}$, owing to the reparameterization described
in~\ref{subsec:reparam}.  To approximately verify~\eqref{eq:bellman_A}, the
corresponding squared residual is minimized by an approximate gradient descent.
The corresponding update equations when learning from incoming transitions of
an exploratory trajectory are
\begin{align}
	\delta Q^k_\deltat &= A(s^k, a^k) - \frac{r^k \deltat + \gamma^{\deltat} V(s^{k}+\delta s^{k}) - V(s^k)}{\deltat}\\
	\theta^{k+1}_\deltat &= \theta^k_\deltat + \eta^1_\deltat \partial_{\theta} V(s^k) \delta Q^k_\deltat\\
	\psi^{k+1}_\deltat &= \psi^k_\deltat + \eta^2_\deltat \partial_{\psi} A(s^k, a^k) \delta Q^k_\deltat.
	\label{eq:approx_bellman_A}
\end{align}
where $\eta$'s are learning rates. In practice, $A$ and $V$ are learned using
transitions sampled from a replay buffer instead of trajectory samples, to
prevent excessive correlation between training samples~\cite{dqn}. Pseudocode
for the discrete actions algorithm is given in Alg.~\ref{alg:dau}. Pseudocode
for the continuous actions algorithm is given in the supplementary material.
\begin{algorithm}[ht]
	\caption{Deep Advantage Updating (Discrete actions)}
	\input{dauc.tex}
	\label{alg:dau}
\end{algorithm}

@@

The updates equations on $\theta$ and $\psi$ are described in
Eq.~\eqref{eq:approx_bellman_A}.  To have parameter steps that do not grow
larger or shrink to $0$ as $\deltat \leftarrow 0$, both $\delta \theta^1$ and
$\delta \theta^2$ should verify stochastic differential equations, and notably
have a deterministic component of order $\deltat$. As $\deltat$ goes to $0$,
updates are rephrased as
\begin{align}
	\delta Q^k_\deltat &= A(s^k_\deltat, a^k_\deltat) - r^k_\deltat - \log(\gamma) V(s^k_\deltat) - \partial_s V(s^k_\deltat) \frac{\delta s^k_\deltat}{\deltat}\nonumber \\&- \frac{(\delta s^k_\deltat)^T \partial_{s^2}^2 V(s^k_\deltat) \delta s^k_\deltat}{2\deltat} + \smallo\left(\frac{\eta^1_\deltat}{\sqrt{\deltat}}\right)\\
	\delta \theta^k_\deltat &= \eta^1_\deltat \partial_{\theta} V(s^k_\deltat) \delta Q^k_\deltat + \smallo\left(\frac{\eta^1_\deltat}{\sqrt{\deltat}}\right)\\
	\delta \psi^k_\deltat &= \eta^2_\deltat \partial_{\psi} A(s^k_\deltat) \delta Q^k_\deltat + \smallo\left(\frac{\eta^2_\deltat}{\sqrt{\deltat}}\right).
\end{align}
For parameter updates to follow a stochastic differential equations, one must
have $\eta^1_\deltat = \alpha^1 \deltat$ and $\eta^2_\deltat = \alpha^2
\deltat$. With this choice of learning rates, the limit SDEs are
\begin{align}
	F &= A(s_t, a_t) - r_t - \log(\gamma) V(s_t) - \partial_s V(s_t) f(s_t, a_t)\nonumber\\
	G &= - \partial_s V(s_t, a_t) \Sigma(s_t, a_t)\nonumber\\
	d\theta_t &= (\alpha^1 F  + D \dbt)\partial_{\theta} V(s_t)\nonumber\\
	d\psi_t &= (\alpha^2 F  + D \dbt)\partial_{\psi} A(s_t, a_t)\nonumber.
\end{align}

>>>>

\subsection{Algorithms}
\label{subsec:algorithm}
To learn $V_{\theta}$ and $A_{\psi}$, variants of Q-learning for continuous~\cite{ddpg} and
discrete~\cite{dqn} action spaces are used. In details, $V_{\theta}$ and $A_{\psi}$ are learnt
using approximate version of the following bellman equation, which holds for the true $A^\pi_\deltat$
and $V^\pi_\deltat$,
\begin{align}
	V^{\pi}_\deltat(s) + \deltat A^{\pi}_\deltat(s, a) &= r\deltat + \gamma^{\deltat}  \E_{s'} V^{\pi}_\deltat(s')\label{eq:bellman_A}\\
	A^{\pi}_\deltat(s, \pi(s)) &= 0\label{eq:max_A}
\end{align}
for a greedy exploitation policy $\pi(s) = \text{argmax}_{a'}A^\pi_\deltat(s,
a')$, exactly implemented in the case of discrete actions, and approximated by
a neural network $\pi_\phi(s)$, trained to maximize (an approximation of)
$A^\pi_\deltat(s, \pi_\phi(s))$ in the continuous case.  Eq.~\eqref{eq:max_A}
is directly verified by $A_{\psi}$, owing to the reparameterization
$A_\psi(s, a) = \bar{A}_\psi(s, a) - \bar{A}_\psi(s, \pi(s))$, described
in~\ref{subsec:reparam}.  To approximately verify~\eqref{eq:bellman_A}, the
corresponding squared residual is minimized by an approximate gradient descent.
The corresponding update equations when learning from a transition $(s, a, r, s')$ of
an exploratory trajectory are
\begin{align}
	\delta Q_\deltat &\leftarrow A(s, a) \deltat - \left(r \deltat + \gamma^{\deltat} V(s') - V(s)\right)\\
	\theta_\deltat &\leftarrow \theta_\deltat + \eta^1_\deltat \partial_{\theta} V(s) \frac{\delta Q_\deltat}{\deltat}\\
	\psi_\deltat &\leftarrow \psi_\deltat + \eta^2_\deltat \partial_{\psi} A(s, a) \frac{\delta Q_\deltat}{\deltat}.
	\label{eq:approx_bellman_A}
\end{align}
where $\eta$'s are learning rates. As we will see in the following section,
to obtain a well defined continuous time limit, the learning rates can be rewritten as
$\eta^i_\deltat = \alpha^i \deltat$, where $\alpha^1$ and $\alpha^2$ are independant
of $\deltat$. In practice, $A$ and $V$ are learned using
transitions sampled from a replay buffer instead of trajectory samples, to
prevent excessive correlation between training samples~\cite{dqn}.
\begin{algorithm}[ht]
	\caption{Deep Advantage Updating (Discrete actions)}
	\input{dauc.tex}
	\label{alg:dau}
\end{algorithm}

@@

The updates equations on $\theta$ and $\psi$ are described in
Eq.~\eqref{eq:approx_bellman_A}.  To have parameter steps that do not grow
larger or shrink to $0$ as $\deltat \leftarrow 0$, both $\delta \theta^1$ and
$\delta \theta^2$ should verify stochastic differential equations, and notably
have a deterministic component of order $\deltat$. As $\deltat$ goes to $0$,
updates are rephrased as
\begin{align}
	\delta Q_\deltat &= A(s, a)\deltat - r\deltat - \log(\gamma) V(s)\deltat - \partial_s V(s) \delta s\nonumber \\&- \frac{(\delta s)^T \partial_{s^2}^2 V(s) \delta s}{2} + \smallo\left(\sqrt{\deltat}\right)\\
	\delta \theta_\deltat &= \eta^1_\deltat \partial_{\theta} V(s) \frac{\delta Q_\deltat}{\deltat} + \smallo\left(\frac{\eta^1_\deltat}{\sqrt{\deltat}}\right)\\
	\delta \psi_\deltat &= \eta^2_\deltat \partial_{\psi} A(s) \frac{\delta Q_\deltat}{\deltat} + \smallo\left(\frac{\eta^2_\deltat}{\sqrt{\deltat}}\right).
\end{align}
For parameter updates to follow a stochastic differential equations, one must
have $\eta^1_\deltat = \alpha^1 \deltat$ and $\eta^2_\deltat = \alpha^2
\deltat$. With this choice of learning rates, the limit SDEs are
\begin{align}
	F &= A(s_t, a_t) - r_t - \log(\gamma) V(s_t) - \partial_s V(s_t) f(s_t, a_t)\nonumber\\
	G &= - \partial_s V(s_t, a_t) \Sigma(s_t, a_t)\nonumber\\
	d\theta_t &= (\alpha^1 F  + D \dbt)\partial_{\theta} V(s_t)\nonumber\\
	d\psi_t &= (\alpha^2 F  + D \dbt)\partial_{\psi} A(s_t, a_t)\nonumber.
\end{align}
The full algorithm can now be derived.
Pseudocode for the discrete actions algorithm is given in Alg.~\ref{alg:dau}.
Pseudocode for the continuous actions algorithm is given in the supplementary
material.
\TODO{Be careful when using RMSprop. When you are facing a stochastic environment
	RMSprop evaluates the second momentum of gradients and rescale gradients by its
	square root. This second momentum will
	be of order $\frac{1}{\deltat}$, due to the stochasticity in the environment. Consequently
	all gradient steps are multiplied by $\sqrt{\deltat}$, and learning rates need only be
multiplied by $\sqrt{\deltat}$ instead of $\deltat$. Taking batches of size proportional to $\frac{1}{\deltat}$
applies a similar fix.}
